### 2024-02-16 documentation/thesis/thesis_abstract.tex

To evaluate the software framework and hardware, two digital sensors
were characterised and tested under the same conditions for noise,
temperature dependence and linearity. The result is that both sensors
can only be used under certain conditions, as the noise intensity is
higher than the specified 50 mühT and the value ranges fluctuate too
much as a result. It is recommended to consider analogue sensors or NMR
probes in the future.

>>>>

To evaluate the software framework and hardware, two digital sensors
were characterised and tested under the same conditions for noise,
temperature dependence and linearity. The result is that both sensors
can only be used under certain conditions, as the noise intensity is
higher than the specified 50 \(\mu\)T and the value ranges fluctuate too
much as a result. It is recommended to consider analogue sensors or NMR
probes in the future.

### 2024-02-16 documentation/thesis/thesis_document.tex
.

@@

\begin{itemize}
\tightlist
\item
  folgendes setup woird für eine vermessung nach der sensor auswertung
  emholen:
\item
  temperaturkomensation sowie linearitäts kompensation mit separaten
  temperatur sensor
\end{itemize}

are they suitable for <1000(+\gls{ppm}) ?

\begin{itemize}
\item
  https://onlinelibrary.wiley.com/doi/epdf/10.1002/mrm.28396
\item
  27cm / 50mT bore
\item
  nmr probes for better results
\item
  mit software calibrierung ist es möglich vermutlich möglich sowie
  mittelung ist es möglich auch mit dem tlv493d kanpp unter die 50uT zu
  kommen
\item
  mess durchläufe mit ist es mögloch von 175uT nach 70uT zu kommen mit
  avg=20 kommt man auf 45
\item
  sollte ein geeignerter ersatzsensor gefunden werden
\item
  beide sensoren sind jedoch durch chrakterisierung von
  permanentmagneten geeignet
\item
  beim tlv493d ist es möglich absolut werte zu erfassen.
\item
  beim mmc ist es möglich relativ magnete untereinander zu vergleichen
\end{itemize}

>>>>

The \emph{TLV493D}, on the other hand, is able to measure these
directly, but does not achieve the required accuracy due to strong noise
and steep temperature coefficients.

@@

After analysing the measurement results, it can be seen that the
selected sensors are only partially suitable for the previously defined
requirements.

In general, further digital and analogue sensors should be characterised
with the developed framework. In particular, the use of analogue
Hallbach sensors with separate bias voltage should be evaluated, as a
simplified characterisation procedure can be applied due to the lack of
a base offset.

In the following, methods will be shown with which it is nevertheless
possible to use these sensors.

\hypertarget{permanent-magnet-charakterisation}{%
\subsubsection{Permanent Magnet
charakterisation}\label{permanent-magnet-charakterisation}}

Both sensors are suitable for precisely measuring and quantifying
magnetic fields. To ensure the linearity of the sensors, compensation
can be performed using a defined measurement setup. This concept has
already been successfully realised with implemented
\ref{example-sensors}, in particular \emph{1D: Single Sensor}
\ref{d-single-sensor}, and proven to be functional in earlier chapters.

The \emph{MMC5603NJ} sensor has a limited measuring range, which means
that it may not the best choise for this application parameters.
However, this limitation also makes it possible to compare relative
magnetic field strengths with each other. Furthermore, by using
software, it is possible to achieve absolute comparability of the
magnetic fields by scaling the measured values accordingly. This was
shown in the chapter \emph{Usecase Evaluation} \ref{usecase-evaluation}
by comparing and sorting different permanent magnets using these
sensors.

Overall, both the \emph{TLV493D} and the \emph{MMC5603NJ} offer
possibilities for characterising permanent magnets. By using suitable
hardware setup, software calibration methods and precise
characterisations can be carried out.

\hypertarget{homogeneity-measurement-of-a-halbach-ring-based-b0-field}{%
\subsubsection{Homogeneity Measurement of a Halbach ring-based B0
field}\label{homogeneity-measurement-of-a-halbach-ring-based-b0-field}}

The \emph{MMC5603NJ} cannot be used here due to the limited value range.
The method of increasing the distance, as with permanent magnet
characterisation, cannot be used here as the magnet is located within a
limited space in the Halbach ring.

In contrast, the \emph{TLV493D} has too much noise, so that the measured
values cannot be used directly without post-processing. With software
calibration, it is probably possible to reduce the noise to below
50\(\mu\)T with the \emph{TLV493D}. As a test, several further
measurement runs were carried out, which achieved results for the sensor
noise of 71\(\mu\)T to 41\(\mu\)T when averaging \emph{100} measured
values and \emph{1000} measured values. However, further measurement
runs must be carried out to verify these results.

In general post-processing of the measurements should, include
temperature compensation with a separate temperature sensor, especially
in the case of changing measurement conditions (e.g.~movement of the
sensor in the B0 field).
